---
title: "Untitled"
author: "Noah Parker"
date: "2024-12-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(knitr)
library(dplyr)
library(kableExtra)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
test.table <- read_csv("~/Desktop/test.table.csv")
print(test.table)
test.table$Prob_t_15
kable(test.table, format = "simple", col.names = c("Starting_State", "First_Event", "Distribution", "Parameters_Estimate", "Total_Probability", "Probability_at_t = 15", "Median_Time_To_Event", "25th%_Time", "75th%_Time"), align = "c")  

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
